Food-web structure, stochasticity and response diversity drive temporal community stability in complex communities

### 2023-11-22 _targets.Rmd
Clarify Figure SR

@@

)
```

@@

@@

```{r}
tar_load(pred_stab_comp_rho)
p_pred_sr_rho <- pred_stab_comp_rho %>%
  filter(response == "stab_com") %>%
  mutate(variable = var_replacement()[variable]) %>%
  ggplot(aes(x = rho, y = variable_values, fill = slope)) +
  geom_raster() +
  facet_wrap(~variable, scales = "free_y") +
  coord_cartesian(expand = FALSE) +
  scale_fill_gradient2(
    low = "red",
    mid = "white",
    high = "blue",
    midpoint = 0,
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill") +
  labs(
    x = "Environmental correlation",
    y = "Food-web structure",
    fill = "Slope Stability-Richness"
    ) +
  theme(
    legend.position = "bottom",
    legend.key.width = unit(2.5, "cm"),
    plot.margin = margin(l = 10, r = 10, unit = "pt")
  )
ggsave_multiple(
  paste0("p_pred_sr_rho", c(".png", ".pdf")),
  plot = p_pred_sr_rho,
  path = here::here("report", "figures"),
  scale = 2.2,
  dpi = 400,
  width = 120,
  height = 120 * .45,
  units = "mm")
```

@@

```
```{r}
p_pred_sr <- plot_grid(
  p_pred_sr_rho_int_env + theme(legend.position = "right"),
  p_pred_sr_rho,
  nrow = 2,
  labels = "auto"
)
ggsave_multiple(
  paste0("p_pred_sr", c(".png", ".pdf")),
  plot = p_pred_sr,
  path = here::here("report", "figures"),
  scale = 2.0,
  dpi = 400,
  width = 120,
  height = 120 * .8,
  units = "mm")
```

>>>>

```{targets r}
  tar_target(p_pop_stab_w_avg_tlvl,
    sim_fw %>%
      filter(env_stoch == .3) %>%
      ggplot(aes(x = w_avg_tlvl, y = log(pop_stab))) +
      geom_point(alpha = .2) +
      geom_smooth(method = "lm") +
      labs(
        x = var_replacement()["w_avg_tlvl"],
        y = var_replacement()["pop_stab"]
        ) +
      theme_bw()
  tar_target(p_pop_stab_h,
    sim_fw %>%
      filter(env_stoch == .3) %>%
      ggplot(aes(x = as.factor(h), y = log(pop_stab))) +
      geom_boxplot(alpha = .2) +
      labs(
        x = var_replacement()["h"],
        y = var_replacement()["pop_stab"]
        ) +
      theme_bw()
  tar_target(p_pop_stab_env_stoch,
    sim_fw %>%
      ggplot(aes(x = as.factor(env_stoch), y = log(pop_stab))) +
      geom_boxplot(alpha = .2) +
      labs(
        x = var_replacement()["env_stoch"],
        y = var_replacement()["pop_stab"]
        ) +
      theme_bw()
  tar_target(p_even_sae_richness,
    sim_fw %>%
      filter(rho == 0) %>%
      ggplot(aes(x = as.factor(richness), y = log(evenness_sae))) +
      geom_boxplot(alpha = .2) +
      geom_smooth(method = "lm") +
      labs(
        x = var_replacement()["richness"],
        y = var_replacement()["evenness_sae"]
        ) +
      theme_bw()
  tar_target(p_sae_total_richness,
    sim_fw %>%
      filter(rho == 0) %>%
      ggplot(aes(x = as.factor(richness), y = log(sae_total))) +
      geom_boxplot(alpha = .2) +
      geom_smooth(method = "lm") +
      scale_x_discrete(breaks = seq(0, 35, 5)) +
      labs(
        x = var_replacement()["richness"],
        y = var_replacement()["sae_total"]
        ) +
      theme_bw()
  tar_target(p_even_sae_w_avg_tlvl,
    sim_fw %>%
      filter(rho == 0) %>%
      ggplot(aes(x = w_avg_tlvl, y = log(evenness_sae))) +
      geom_point(alpha = .2) +
      geom_smooth(method = "lm") +
      labs(
        x = var_replacement()["w_avg_tlvl"],
        y = var_replacement()["evenness_sae"]
        ) +
      theme_bw()
  tar_target(p_sae_total_w_avg_tlvl,
    sim_fw %>%
      filter(rho == 0) %>%
      ggplot(aes(x = w_avg_tlvl, y = log(sae_total))) +
      geom_point(alpha = .2) +
      geom_smooth(method = "lm") +
      labs(
        x = var_replacement()["w_avg_tlvl"],
        y = var_replacement()["sae_total"]
        ) +
      theme_bw()
  tar_target(p_even_sae_avg_int,
    sim_fw %>%
      filter(rho == 0) %>%
      ggplot(aes(x = avg_int_strength, y = log(evenness_sae))) +
      geom_point(alpha = .2) +
      geom_smooth(method = "lm") +
      labs(
        x = var_replacement()["avg_int_strength"],
        y = var_replacement()["evenness_sae"]
        ) +
      theme_bw()
  tar_target(p_sae_total_avg_int,
    sim_fw %>%
      filter(rho == 0) %>%
      ggplot(aes(x = avg_int_strength, y = log(sae_total))) +
      geom_point(alpha = .2) +
      geom_smooth(method = "lm") +
      labs(
        x = var_replacement()["avg_int_strength"],
        y = var_replacement()["sae_total"]
        ) +
      theme_bw()
  tar_target(p_sae_total_ct_alive,
    sim_fw %>%
      filter(rho == 0) %>%
      ggplot(aes(x = ct_alive, y = log(sae_total))) +
      geom_point(alpha = .2) +
      geom_smooth(method = "lm") +
      labs(
        x = var_replacement()["ct_alive"],
        y = var_replacement()["sae_total"]
        ) +
      theme_bw()
  tar_target(p_cpe_int_avg_int,
    sim_fw %>%
      ggplot(aes(x = avg_int_strength, y = log(cpe_int))) +
      geom_point(alpha = .2) +
      geom_smooth(method = "lm") +
      labs(
        x = var_replacement()["avg_int_strength"],
        y = var_replacement()["cpe_int"]
        ) +
      theme_bw()
  tar_target(p_cpe_avg_int,
    sim_fw %>%
      ggplot(aes(x = avg_int_strength, y = log(cpe))) +
      geom_point(alpha = .2) +
      geom_smooth(method = "lm") +
      labs(
        x = var_replacement()["avg_int_strength"],
        y = var_replacement()["cpe"]
        ) +
      theme_bw()
  tar_target(p_cpe_rho,
    sim_fw %>%
      ggplot(aes(x = rho, y = log(cpe), group = rho)) +
      geom_boxplot() +
      labs(
        x = var_replacement()["rho"],
        y = var_replacement()["cpe"]
        ) +
      theme_bw()
  tar_target(p_sem_bivariate_relations,
    plot_grid(
      p_pop_stab_w_avg_tlvl, p_pop_stab_h, p_pop_stab_env_stoch,
      p_sae_total_richness, p_sae_total_ct_alive, p_sae_total_w_avg_tlvl,
      p_sae_total_avg_int, p_cpe_avg_int, p_cpe_rho

```{r}

@@

    )
)
```

@@

```{r}
ggsave_multiple(
  paste0("p_sem_bivariate_relations", c(".png", ".pdf")),
  plot = tar_read(p_sem_bivariate_relations),
  path = here::here("report", "figures"),
  scale = 3,
  dpi = 400,
  width = 80,
  height = 80 * .9,
  units = "mm")
```

@@

```{r}
tar_load(pred_stab_comp_rho)
p_pred_sr_rho <- pred_stab_comp_rho %>%
  filter(response == "stab_com") %>%
  mutate(
    variable = var_replacement()[variable],
    resp_div = 1 - rho
    ) %>%
  ggplot(aes(x = resp_div, y = variable_values, fill = slope)) +
  geom_raster() +
  facet_wrap(~variable, scales = "free_y") +
  coord_cartesian(expand = FALSE) +
  scale_fill_gradient2(
    low = rho_cat_colors()["Low"],
    mid = "white",
    high = rho_cat_colors()["High"],
    midpoint = 0,
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill") +
  labs(
    x = var_replacement()["resp_div"],
    y = "Food-web structure",
    fill = "Slope community stability - Richness"
    ) +
  theme(
    legend.position = "bottom",
    legend.key.width = unit(2.5, "cm"),
    plot.margin = margin(l = 10, r = 10, unit = "pt")
  )
ggsave_multiple(
  paste0("p_pred_sr_rho", c(".png", ".pdf")),
  plot = p_pred_sr_rho,
  path = here::here("report", "figures"),
  scale = 2.2,
  dpi = 400,
  width = 120,
  height = 120 * .45,
  units = "mm")
```

@@

```{r}
pred_data_sr_fw <- pred_data %>%
  filter(
    ct_alive %in% c(.1, .3),
    rho %in% c(0, .75),
    richness >= 1,
    Z == 100,
    h %in% c(2),
    avg_int_strength %in% c(.01, .1),
    env_stoch == .1,
    w_avg_tlvl %in% c(2.0, 3.0)
    ) %>%
mutate(
  group_ct_alive = case_when(
    ct_alive == .3 & avg_int_strength == .01 & w_avg_tlvl == 2.0 ~ "High",
    ct_alive == .1 & avg_int_strength == .01 & w_avg_tlvl == 2.0 ~ "Low"
    ),
  group_avg_int_strength = case_when(
    ct_alive == .1 & avg_int_strength == .1 & w_avg_tlvl == 2.0 ~ "High",
    ct_alive == .1 & avg_int_strength == .01 & w_avg_tlvl == 2.0 ~ "Low"
    ),
  group_w_avg_tlvl = case_when(
    ct_alive == .1 & avg_int_strength == .01 & w_avg_tlvl == 3.0 ~ "High",
    ct_alive == .1 & avg_int_strength == .01 & w_avg_tlvl == 2.0 ~ "Low"
    )) %>%
pivot_longer(starts_with("group_")) %>%
filter(!is.na(value)) %>%
mutate(name = str_remove(name, "group_"))
p_pred_data_sr_fw <- pred_data_sr_fw %>%
  mutate(name = var_replacement()[name]) %>%
  ggplot(aes(
      x = richness, y = stab_com,
      color = resp_div,
      fill = resp_div,
      linetype = value,
      #alpha = as.factor(avg_int_strength)
      )) +
  geom_line(linewidth = .8) +
  geom_ribbon(
    aes(ymin = stab_com - stab_com_se, ymax = stab_com + stab_com_se),
    alpha = .3, color = NA) +
  scale_color_manual(values = rho_cat_colors()) +
  scale_fill_manual(values = rho_cat_colors()) +
  facet_grid(cols = vars(name)) +
  labs(
    x = var_replacement()["richness"],
    y = var_replacement()["stab_com"],
    fill = var_replacement()["resp_div"],
    color = var_replacement()["resp_div"],
    linetype = "Food-web structure value"
  ) +
  theme_bw() +
  theme(legend.position = "bottom") +
  guides(
    linetype = guide_legend(keywidth = 2,
      override.aes = list(fill = NA, alpha = 1)
      ),
    fill = guide_legend(override.aes = list(linetype = 0, alpha = 1))
  )

ggsave_multiple(
  paste0("p_pred_data_sr_fw", c(".png", ".pdf")),
  plot = p_pred_data_sr_fw,
  path = here::here("report", "figures"),
  scale = 3,
  dpi = 400,
  width = 80,
  height = 80 * .4,
  units = "mm")
```

## Figure SR

```{r}
p_pred_sr <- plot_grid(
  p_pred_data_sr_fw + theme(legend.position = "right"),
  p_pred_sr_rho,
  nrow = 2,
  rel_heights = c(.7, 1),
  labels = "auto"
)
ggsave_multiple(
  paste0("p_pred_sr", c(".png", ".pdf")),
  plot = p_pred_sr,
  path = here::here("report", "figures"),
  scale = 2.0,
  dpi = 400,
  width = 120,
  height = 120 * .7,
  units = "mm")
```

### 2023-11-22 paper/manuscript.Rmd
Clarify Figure SR

---
title: Food-web structure, stochasticity and response diversity drive temporal community stability in complex communities
author: Alain Danet, (Sonia Kéfi, Thomas F Johnson), Andrew P. Beckerman
output:
  officedown::rdocx_document:
    base_format: "bookdown::word_document2"
    number_sections: false
  bookdown::pdf_document2:
    latex_engine: xelatex
    keep_tex: true
    spacing: double
    number_sections: false
always_allow_html: true
bibliography: references.bib
link-citations: true
toc: false
linestretch: 2.0
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
  - \hypersetup{backref=true}
  - \usepackage{setspace}\doublespacing
---

@@

```{r, results = FALSE}
sapply(c("targets", "tidyverse", "magrittr", "cowplot", "here", "piecewiseSEM",
    "semEff", "ggcorrplot", "kableExtra", "officedown"),
  require,
  character.only = TRUE)

mytheme <- theme_cowplot(font_size = 8) +
background_grid() +
theme(legend.position = "bottom")
theme_set(mytheme)
sapply(list.files(here("R"), full.names = TRUE), source)
```

@@

```{r}
sem_cap <- paste0(
  "Structural Equation Model linking initial model parameters to resulting
  temporal stability of biomass. Arrows display positive (continuous) and
  negative (dashed) standardised effects. Initial parameters were initial
  species richness, initial connectance, Prey-Predator Mass Ratio (PPMR), hill
  exponent, variance of stochastic mortality rates (Env. stochasticity), and
  cross-correlation among species mortality rates (Env. correlation). We only
  displayed standardised coefficients whose absolute values are superior to 0.1
  are displayed. SEM containing containing further partition of Statistical
  Averaging Effect and Compensatory effects is displayed in Fig. SXX.")
```

```{r sem, fig.cap=sem_cap}
knitr::include_graphics(here("report", "figures", "sem_stab_simplified.pdf"))
```

@@

```{r semtot, fig.cap = semtot_cap}
knitr::include_graphics(here::here("report", "figures", "p_sem_tot_stab.png"))
```

@@

```{r pred, fig.cap = pred_cap}
knitr::include_graphics(here("report", "figures", "p_pred_sr.pdf"))
```

>>>>

---
title: Food-web structure, stochasticity and response diversity drive temporal community stability in complex communities
author: "Alain Danet, (Sonia Kéfi, Thomas F Johnson), Andrew P. Beckerman"
date: ""
output:
  officedown::rdocx_document:
    base_format: "bookdown::word_document2"
    number_sections: false
  bookdown::pdf_document2:
    latex_engine: xelatex
    keep_tex: true
    spacing: double
    number_sections: false
always_allow_html: true
bibliography: references.bib
link-citations: true
toc: false
linestretch: 2.0
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
  - \hypersetup{backref=true}
  - \usepackage{setspace}\doublespacing
---

@@

```{r, results = FALSE}
sapply(c("targets", "tidyverse", "magrittr", "cowplot", "here", "piecewiseSEM",
    "semEff", "ggcorrplot", "kableExtra", "rmarkdown", "officedown"),
  require,
  character.only = TRUE)
mytheme <- theme_cowplot(font_size = 8) +
background_grid() +
theme(legend.position = "bottom")
theme_set(mytheme)
sapply(list.files(here("R"), full.names = TRUE), source)
```

@@

```{r}
sem_cap <- paste0(
  "Structural Equation Model linking initial model parameters to resulting
  temporal stability of biomass. Arrows display positive (continuous) and
  negative (dashed) standardised effects. Initial parameters were initial
  species richness, initial connectance, Prey-Predator Mass Ratio (PPMR), hill
  exponent, variance of stochastic mortality rates (Env. stochasticity), and
  cross-correlation among species mortality rates (Env. correlation). We only
  displayed standardised coefficients whose absolute values are superior to 0.1
  are displayed. A more complete SEM containing further partition of Statistical
  Averaging Effect and Compensatory effects is displayed in Fig. SXX.")
```

```{r sem, fig.cap=sem_cap, fig.id = "sem"}
knitr::include_graphics(here("report", "figures", "sem_stab_simplified.pdf"))
```

@@

```{r semtot, fig.cap = semtot_cap, fig.id = "semtot"}
knitr::include_graphics(here::here("report", "figures", "p_sem_tot_stab.png"))
```

@@

```{r pred, fig.cap = pred_cap, fig.id = "pred"}
knitr::include_graphics(here("report", "figures", "p_pred_sr.pdf"))
```
